Shader Pipeline and Effect Encapsulation using CLOS

### 2019-01-29 els2019-shader-pipeline/paper.tex
Add CCS

\begin{CCSXML}
  %% FIXME: CCS
\end{CCSXML}

>>>>

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10011007.10010940.10010971.10010972.10010979</concept_id>
  <concept_desc>Software and its engineering~Object oriented architectures</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10011007.10010940.10010971.10011682</concept_id>
  <concept_desc>Software and its engineering~Abstraction, modeling and modularity</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10011007.10011006.10011066.10011067</concept_id>
  <concept_desc>Software and its engineering~Object oriented frameworks</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010371</concept_id>
  <concept_desc>Computing methodologies~Computer graphics</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10011007.10011006.10011041.10011688</concept_id>
  <concept_desc>Software and its engineering~Parsers</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Object oriented architectures}
\ccsdesc[300]{Software and its engineering~Abstraction, modeling and modularity}
\ccsdesc[300]{Software and its engineering~Object oriented frameworks}
\ccsdesc[300]{Computing methodologies~Computer graphics}
\ccsdesc[100]{Software and its engineering~Compilers}
